---
title: "SETx ERGM"
output: html_document
date: "2024-02-11"
---



# Exponetial Random Graph Models

## ERGM-SETx All Issues

Our second approach is to reduce the network to only those who reported risk and impacts.

```{r g_out}
g_out<-igraph::degree(g1,mode="out")
V(g1)$outdegree<-g_out
g1_no_out<-delete_vertices(g1, V(g1)[outdegree==0])
a1<-read.csv("a1.csv")



# Remove the column named 'precip'
a1 <- a1[ , !(names(a1) %in% c("precip"))]

gvis_no_out<-toVisNetworkData(g1_no_out)
nodelist_no_out<-gvis_no_out$nodes

a2<-as.data.frame(nodelist_no_out)



# Perform left join with different column names
a2 <- left_join(a2, a1, by = "id" )
a2<-a2[-c(3:4)]
a2 <- a2 %>% mutate(precip = precip.1)

```


https://statnet.org/Workshops/ergm_tutorial.html#7_Diagnostics:\_troubleshooting_and_checking_for_model_degeneracy

First let's build a network object and model that accounts for the full network of 61 nodes that includes the data imputation.

gwdsp(decay, fixed=FALSE, cutoff=30) (binary) (directed) (undirected) (curved) Geometrically weighted dyadwise shared partner distribution: This term adds one network statistic to the model equal to the geometrically weighted dyadwise shared partner distribution with decay parameter decay parameter, which should be non-negative. The value supplied for this parameter may be fixed (if fixed=TRUE), or it may be used instead as the starting value for the estimation of decay in a curved exponential family model (when fixed=FALSE, the default) (see Hunter and Handcock, 2006). This term can be used with directed and undirected networks.

For directed networks, only outgoing two-path ("OTP") shared partners are counted. In other words, for a (directed) dyad (i,j) in a directed graph, the number of shared partners counted by gwdsp is the number of nodes k that have edges i -\> k -\> j. (These may also be called homogeneous shared partners.) To count other types of shared partners instead, see dgwdsp.

The optional argument cutoff sets the number of underlying DSP terms to use in computing the statistics when fixed=FALSE, in order to reduce the computational burden. Its default value can also be controlled by the gw.cutoff term option control parameter. (See control.ergm.).

"dyadwise shared partners" means: how many common neighbors do two vertices have? It's a trivial matrix operation that's easily implemented in any scientific computing system (including R): square the adjacency matrix and discard the diagonal.

"edgewise shard partners" means: how many common neighbors do two connected vertices have? Thus the same and above, but mask the squared adjacency matrix with the original one.

The GWESP is similar to a triangles parameter (the number of closed triangles in a model, with the distinction that the GWESP is less susceptible to model degeneracy. If one of your parameters in the estimation does a similar thing to the GWESP (e.g. a homophily term), then there can be a high correlation between the parameters.

```{r SETx full network object build}
neta1<-a1
neta1 <- mutate(a1, org_type = case_when(
    org_type == "Nonprofit" ~ "Nonprofit",
    org_type == "Academia" ~ "Academia",
    org_type == "County agency" ~ "Local Gov",
    org_type == "State agency" ~ "State Gov",
    org_type == "Federal agency" ~ "Fed Gov",
    org_type == "Municipal" ~ "Local Gov",
    org_type == "Other" ~ "State Gov"
    
  ))

neta1$org_type <-
  factor(neta1$org_type, levels = c("Local Gov", "State Gov", "Fed Gov", "Nonprofit", "Academia"))

table(neta1$org_type)


# Function to impute missing values with the mean of the org_type group
impute_with_group_mean <- function(data, attribute, group) {
  data[[attribute]] <- ave(data[[attribute]], data[[group]], FUN = function(x) {
    ifelse(is.na(x), mean(x, na.rm = TRUE), x)
  })
  return(data)
}

# Impute missing values for Confident and Information based on org_type
neta1 <- impute_with_group_mean(neta1, "Confident", "org_type")
neta1 <- impute_with_group_mean(neta1, "Information", "org_type")




g1<-simplify(g1)
setxnet <- as.network(x = as_edgelist(g1),
# collab_edges is the edge list created in the V3_SETx Network Analysis.qmd
                        directed = TRUE,
# specify whether the network is directed
                        matrix.type="edgelist",
                        loops = FALSE)

#org demographics
set.vertex.attribute(setxnet, "name", neta1[,1])
set.vertex.attribute(setxnet, "org type", as.character(neta1$org_type))

#drivers of risk
set.vertex.attribute(setxnet, "precip.1", as.numeric(neta1$precip))
set.vertex.attribute(setxnet, "topography", as.numeric(neta1$topography))
set.vertex.attribute(setxnet, "infrastructure_driver", as.numeric(neta1$infrastructure_driver))
set.vertex.attribute(setxnet, "pop_growth", as.numeric(neta1$pop_growth))
set.vertex.attribute(setxnet, "socio_economic", as.numeric(neta1$socio_economic))

#prioritize impacts
set.vertex.attribute(setxnet, "ecological", as.numeric(neta1$ecological))
set.vertex.attribute(setxnet, "economic", as.numeric(neta1$economic))
set.vertex.attribute(setxnet, "infrastructure_impact", as.numeric(neta1$infrastructure_impact))
set.vertex.attribute(setxnet, "social_equity", as.numeric(neta1$social_equity))
set.vertex.attribute(setxnet, "Confident", as.numeric(neta1$Confident))
set.vertex.attribute(setxnet, "Information", as.numeric(neta1$Information))

#alternatively, this code will input vector info
#setxnet%v%"precip" <- as.numeric(neta1$precip)

#Bernoulli null
setxnetmodel.01<-ergm(setxnet~edges,control=control.ergm(MCMLE.maxit=2))
summary(setxnetmodel.01)

# 
# # Identify vertices with missing precip.1 values
# vertices_to_remove <- which(is.na(setxnet %v% "precip.1"))
# 
# # Remove these vertices from the network
# setxnet <- delete.vertices(setxnet, vertices_to_remove)


#all impact and driver variables 
set.seed(1021221)

setxnetmodel.all<-ergm(setxnet~
                          edges+
                          gwesp(decay = .5, fixed = T)+
                          gwidegree(decay = 1, fixed = T)+
                          nodematch("org type")+
                          nodecov("ecological")+
                          absdiff("ecological")+
                          nodecov("economic")+
                          absdiff("economic")+
                          nodecov("infrastructure_impact")+
                          absdiff("infrastructure_impact")+
                          nodecov("social_equity")+
                          absdiff("social_equity")+
                          nodecov("precip.1")+
                          absdiff("precip.1")+
                          nodecov("topography")+
                          absdiff("topography")+
                          nodecov("infrastructure_driver")+
                          absdiff("infrastructure_driver")+
                          nodecov("pop_growth")+
                          absdiff("pop_growth")+
                          nodecov("socio_economic")+
                          absdiff("socio_economic") +
                          nodecov("Confident") +
                          absdiff("Confident") +
                          nodecov("Information") +
                          absdiff("Information"),
                          control = control.ergm(MCMLE.density.guard = 200, 
                                    
                                                 MCMLE.maxit = 2,
                                                 MCMLE.effectiveSize=NULL,
                                                 MCMC.interval = 10000),
                                                 verbose=T)
                                                 
# # Reset graphical parameters
# graphics.off()
# 
# # Set plot layout and adjust margins
# par(mfrow = c(1, 1))
# par(mar = c(8, 8, 8, 8))
# 
# # Open a new larger plotting window using x11()
# x11(width = 12, height = 12)

# Run MCMC diagnostics
#mcmc.diagnostics(setxnetmodel.all)

# Summary of the model
summary(setxnetmodel.all)

# # Goodness of Fit analysis
mod.fit <- gof(setxnetmodel.all, GOF = ~ distance + espartners + idegree + odegree)
summary(mod.fit)
# 
# # Plot the GOF results
# par(mfrow = c(2, 2))
# plot(mod.fit, main = "GOF - Drivers")
# par(mfrow = c(1, 1))
# 
# # Save MCMC diagnostics to a file if necessary
# png("mcmc_diagnostics.png", width = 1200, height = 1200)
#mcmc.diagnostics(setxnetmodel.all)
# dev.off()
```

## ERGM-SETx Prepare and Mitigate

```{r}
g1_prepare<-simplify(g1_pr)
setxnet_pre <- as.network(x = as_edgelist(g1_prepare),
                      # collab_edges is the edge list created in the V3_SETx Network Analysis.qmd
                      directed = TRUE,
                      # specify whether the network is directed
                      matrix.type="edgelist",
                      loops = FALSE)

#org demographics
set.vertex.attribute(setxnet_pre, "name", neta1[,1])
set.vertex.attribute(setxnet_pre, "org type", as.character(neta1$org_type))

#drivers of risk
set.vertex.attribute(setxnet_pre, "precip", as.numeric(neta1$precip))
set.vertex.attribute(setxnet_pre, "topography", as.numeric(neta1$topography))
set.vertex.attribute(setxnet_pre, "infrastructure_driver", as.numeric(neta1$infrastructure_driver))
set.vertex.attribute(setxnet_pre, "pop_growth", as.numeric(neta1$pop_growth))
set.vertex.attribute(setxnet_pre, "socio_economic", as.numeric(neta1$socio_economic))

#prioritize impacts
set.vertex.attribute(setxnet_pre, "ecological", as.numeric(neta1$ecological))
set.vertex.attribute(setxnet_pre, "economic", as.numeric(neta1$economic))
set.vertex.attribute(setxnet_pre, "infrastructure_impact", as.numeric(neta1$infrastructure_impact))
set.vertex.attribute(setxnet_pre, "social_equity", as.numeric(neta1$social_equity))
set.vertex.attribute(setxnet_pre, "Confident", as.numeric(neta1$Confident))
set.vertex.attribute(setxnet_pre, "Information", as.numeric(neta1$Information))

#alternatively, this code will input vector info
#setxnet_pre%v%"precip" <- as.numeric(neta1$precip)

#Bernoulli null
setxnet_premodel.01<-ergm(setxnet_pre~edges,control=control.ergm(MCMLE.maxit=2))
summary(setxnet_premodel.01)

# # Identify vertices with missing precip values
# vertices_to_remove <- which(is.na(setxnet_pre %v% "precip"))
# 
# # If you want to remove these vertices:
# setxnet_pre <- delete.vertices(setxnet_pre, vertices_to_remove)


#all impact and driver variables 
set.seed(1021)

setxnet_prepare.all <- ergm(setxnet_pre~
                            edges+
                            gwesp(decay = .5, fixed = FALSE, cutoff=50)+
                            gwidegree(decay = 1, fixed = FALSE, cutoff=50)+
                         nodematch("org type")+
                         nodecov("ecological")+
                         absdiff("ecological")+
                         nodecov("economic")+
                         absdiff("economic")+
                         nodecov("infrastructure_impact")+
                         absdiff("infrastructure_impact")+
                         nodecov("social_equity")+
                         absdiff("social_equity")+
                         nodecov("precip")+
                         absdiff("precip")+
                         nodecov("topography")+
                         absdiff("topography")+
                         nodecov("infrastructure_driver")+
                         absdiff("infrastructure_driver")+
                         nodecov("pop_growth")+
                         absdiff("pop_growth")+
                         nodecov("socio_economic")+
                          absdiff("socio_economic") +
                          nodecov("Confident") +
                          absdiff("Confident") +
                          nodecov("Information") +
                          absdiff("Information"),

  control = control.ergm(
  MCMLE.density.guard = 200, 
  MCMLE.maxit = 1,
  MCMLE.effectiveSize = 500,
  MCMC.interval = 10000,
  SA.burnin = 1000,       # Simulated Annealing burn-in period

),
                                                 verbose=T)
# # Reset graphical parameters
# graphics.off()
# 
# # Set plot layout and adjust margins
# par(mfrow = c(1, 1))
# par(mar = c(5, 4, 4, 2) + 0.1)
# 
# # Open a new larger plotting window using x11()
# x11(width = 12, height = 12)

# Run MCMC diagnostics
#mcmc.diagnostics(setxnet_prepare.all)

# Summary of the model
summary(setxnet_prepare.all)

# # Goodness of Fit analysis
mod.fit <- gof(setxnet_prepare.all, GOF = ~ distance + espartners + idegree + odegree)
summary(mod.fit)
# 
# # Plot the GOF results
# par(mfrow = c(2, 2))
# plot(mod.fit, main = "GOF - Drivers")
# par(mfrow = c(1, 1))
# 
# # Save MCMC diagnostics to a file if necessary
# png("mcmc_diagnostics.png", width = 1200, height = 1200)
# mcmc.diagnostics(setxnet_prepare.all)
# dev.off()
```

## ERGM-SETx Respond, Recover, Rebuild

```{r}
g1_respond<-simplify(g1_rr)
setxnet_rrr <- as.network(x = as_edgelist(g1_respond),
                          # collab_edges is the edge list created in the V3_SETx Network Analysis.qmd
                          directed = TRUE,
                          # specify whether the network is directed
                          matrix.type="edgelist",
                          loops = FALSE)

#org demographics
set.vertex.attribute(setxnet_rrr, "name", neta1[,1])
set.vertex.attribute(setxnet_rrr, "org type", as.character(neta1$org_type))

#drivers of risk
set.vertex.attribute(setxnet_rrr, "precip", as.numeric(neta1$precip))
set.vertex.attribute(setxnet_rrr, "topography", as.numeric(neta1$topography))
set.vertex.attribute(setxnet_rrr, "infrastructure_driver", as.numeric(neta1$infrastructure_driver))
set.vertex.attribute(setxnet_rrr, "pop_growth", as.numeric(neta1$pop_growth))
set.vertex.attribute(setxnet_rrr, "socio_economic", as.numeric(neta1$socio_economic))

#prioritize impacts
set.vertex.attribute(setxnet_rrr, "ecological", as.numeric(neta1$ecological))
set.vertex.attribute(setxnet_rrr, "economic", as.numeric(neta1$economic))
set.vertex.attribute(setxnet_rrr, "infrastructure_impact", as.numeric(neta1$infrastructure_impact))
set.vertex.attribute(setxnet_rrr, "social_equity", as.numeric(neta1$social_equity))
set.vertex.attribute(setxnet_rrr, "Confident", as.numeric(neta1$Confident))
set.vertex.attribute(setxnet_rrr, "Information", as.numeric(neta1$Information))

#alternatively, this code will input vector info
setxnet_rrr%v%"precip" <- as.numeric(neta1$precip)

#Bernoulli null
setxnet_rrrmodel.01<-ergm(setxnet_rrr~edges,control=control.ergm(MCMLE.maxit=2))
summary(setxnet_rrrmodel.01)

# # Identify vertices with missing precip values and remove them
# vertices_to_remove <- which(is.na(setxnet_rrr %v% "precip"))
# setxnet_rrr <- delete.vertices(setxnet_rrr, vertices_to_remove)


#all impact and driver variables 
set.seed(1021221)

setxnet_respond.all<-ergm(setxnet_rrr~
                            edges+
                            gwesp(decay = .5, fixed = FALSE, cutoff=50)+
                            gwidegree(decay = 1, fixed = FALSE, cutoff=50)+
                            nodematch("org type")+
                            nodecov("ecological")+
                            absdiff("ecological")+
                            nodecov("economic")+
                            absdiff("economic")+
                            nodecov("infrastructure_impact")+
                            absdiff("infrastructure_impact")+
                            nodecov("social_equity")+
                            absdiff("social_equity")+
                            nodecov("precip")+
                            absdiff("precip")+
                            nodecov("topography")+
                            absdiff("topography")+
                            nodecov("infrastructure_driver")+
                            absdiff("infrastructure_driver")+
                            nodecov("pop_growth")+
                            absdiff("pop_growth")+
                            nodecov("socio_economic")+
                          absdiff("socio_economic") +
                          nodecov("Confident") +
                          absdiff("Confident") +
                          nodecov("Information") +
                          absdiff("Information"),
                                      constraints = ~ bd(maxout = 50),   
  control = control.ergm(
  MCMLE.density.guard = 200, 
  MCMLE.maxit = 1,
  MCMLE.effectiveSize = 500,
  MCMC.interval = 80000,
  SA.burnin = 1000,       # Simulated Annealing burn-in period

),
                                                 verbose=T)
# graphics.off()
# 
# # Set plot layout and adjust margins
# par(mfrow = c(1, 1))
# par(mar = c(5, 4, 4, 2) + 0.1)
# 
# # Open a new larger plotting window using x11()
# x11(width = 12, height = 12)
# 
# # Run MCMC diagnostics
#mcmc.diagnostics(setxnet_respond.all)

# Summary of the model
summary(setxnet_respond.all)

# # Goodness of Fit analysis
mod.fit <- gof(setxnet_respond.all, GOF = ~ distance + espartners + idegree + odegree)
summary(mod.fit)
# 
# # Plot the GOF results
# par(mfrow = c(2, 2))
# plot(mod.fit, main = "GOF - Respond")
# par(mfrow = c(1, 1))
# 
# # Save MCMC diagnostics to a file if necessary
# png("mcmc_diagnostics_respond.png", width = 1200, height = 1200)
# mcmc.diagnostics(setxnet_respond.all)
# dev.off()

``` 


```{r ergm-diagnostics-and-gof, fig.width=12, fig.height=10}
# 1. Extract raw MCMC sample matrix
chain_mat <- as.matrix(setxnetmodel.all$sample)

# 2. Panels a–f: diagnostics
par(mfrow = c(2, 3), mar = c(4, 4, 2, 1))

# a–c: trace plots for stats 1–3
for (i in 1:3) {
  xi <- chain_mat[, i]
  plot(xi, type = "l",
       xlab = "Iteration",
       ylab = "",
       main = paste0(letters[i], ": ", colnames(chain_mat)[i]))
}

# d–f: running standard error (sd up to t / sqrt(t))
for (i in 1:3) {
  xi     <- chain_mat[, i]
  run_sd <- sapply(seq_along(xi), function(t) if (t > 1) sd(xi[1:t]) else NA)
  run_se <- run_sd / sqrt(seq_along(xi))
  plot(run_se, type = "l",
       xlab = "Iteration",
       ylab = "Running SE",
       main = paste0(letters[3 + i], ": SE ", colnames(chain_mat)[i]))
}

# 3. Panels g–j: goodness-of-fit
mod.fit <- gof(setxnetmodel.all, GOF = ~distance + espartners + idegree + odegree)
par(mfrow = c(2, 2), mar = c(4, 4, 2, 1))
plot(mod.fit)

# Define models
models <- list(
  "All-Issues"       = setxnetmodel.all,
  "Prepare/Mitigate" = setxnet_prepare.all,
  "Respond/Recover"  = setxnet_respond.all
)

# Which parameter to plot
param <- "edges"

# 3 rows (diagnostics) x 3 cols (models)
par(mfrow = c(3, 3), mar = c(4, 4, 2, 1))

# Row 1: Trace plots
for (mod in names(models)) {
  mat <- as.matrix(models[[mod]]$sample)
  xi  <- mat[, param]
  plot(xi, type = "l",
       xlab = "Iteration", ylab = "",
       main = paste("Trace  |", mod))
}

# Row 2: Running standard error
for (mod in names(models)) {
  mat    <- as.matrix(models[[mod]]$sample)
  xi     <- mat[, param]
  run_sd <- sapply(seq_along(xi), function(t) if(t > 1) sd(xi[1:t]) else NA)
  run_se <- run_sd / sqrt(seq_along(xi))
  plot(run_se, type = "l",
       xlab = "Iteration", ylab = "Running SE",
       main = paste("Run SE |", mod))
}

# Row 3: Autocorrelation
for (mod in names(models)) {
  mat <- as.matrix(models[[mod]]$sample)
  xi  <- mat[, param]
  acf(xi, main = paste("ACF    |", mod), sub = "")
}


```
